figures

### 2023-05-10 viz/figures.Rmd
Final published version

# save figure outputs here
knitr::opts_chunk$set(fig.path = here("viz", "figures", ""))

@@

```{r Figure1, fig.width = 12, fig.height = 6}

@@

# layout <- "
# AAA#
# AAAB
# AAA#
# "
# 
# p1 + p2 +
#   plot_layout(design = layout)

@@

```{r Figure2, fig.width = 10, fig.height = 4}

@@

mods$total_mix_full$mdt$marginal %>% 
  bind_rows(., mods$total_mix_full$mpt$marginal) %>% 
  bind_rows(., mods$total_mix_full$cabat$marginal) %>% 
  pivot_wider(names_from = group, values_from = c(predicted:conf.high)) %>% 
  mutate(tone = factor(x, levels = c("Non-tonal", "Pitch-accented", "Tonal")),
         test = factor(test, levels = c("mdt", "mpt", "cabat"))) %>% 
  ggplot(.,
         aes(x = test, y = predicted_No, color = tone)) +
  geom_hline(aes(yintercept = 0), color = "black", alpha = 0.7, linetype = "dashed") +
  geom_errorbar(aes(ymax = conf.high_No, ymin = conf.low_No, color = tone), position = position_dodge(.5), width = .2, key_glyph = draw_key_rect) +
  geom_errorbar(aes(ymax = conf.high_Yes, ymin = conf.low_Yes, color = tone), position = position_dodge(.5), width = .2, alpha = .5, key_glyph = draw_key_rect) +
  geom_point(position = position_dodge(.5), size = 2) +
  geom_point(data = test, aes(x = test, y = predicted, shape = group), inherit.aes = FALSE, alpha = 0) +
  scale_shape_manual(values = c(19, 17), name = "test",
                     labels = c("Without Music Lessons", "With Music Lessons")) +
  geom_point(aes(y = predicted_Yes), position = position_dodge(.5), size = 2, alpha = .5, pch = 17) +
  geom_linerange(aes(ymax = predicted_Yes, ymin = predicted_No, color = tone), position = position_dodge(.5), linetype = "dashed", alpha = .5) +
  scale_x_discrete(labels = c("Melodic Disrimination","Mistuning Perception", "Beat Alignment"), position = "top") +
  scale_color_manual(values=color_scheme, labels = c("Non-tonal","Pitch-accented","Tonal")) +
  guides(shape = guide_legend(override.aes = list(alpha = .8, size = 4))) +
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    axis.text.x = element_text(size = 16),
    panel.grid.major.y = element_line(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(), 
    legend.position = "bottom",
    legend.text = element_text(size = 12))

@@

```{r Figure3, fig.width = 10, fig.height = 6}

lang_plotter <- function(data, x_lab, y_lab = NULL) {
  ggplot(data, aes(x = estimate, y = language, xmin = conf.low, xmax = conf.high, colour = Tone)) +
    geom_vline(xintercept = 0, lty = "dashed", colour = "grey50") + 
    geom_point(size = 0.8) +
    geom_errorbar(size = 0.4) +
    scale_colour_manual(values = c("#85C0F9", "#A95AA1", "#F5793A"),
                        labels = c("Non-tonal","Pitch-accented", "Tonal"),
                        name = NULL) +
    lims(x = c(-0.8,0.8)) +
    labs(
      x = NULL,
      y = y_lab, 
      title = x_lab
    ) +
    theme_minimal() +
    theme(axis.text.y= element_blank(),
          axis.title = element_text(size = 16),
          axis.ticks.y = element_blank(),
          legend.text = element_text(size = 12),
          panel.grid = element_blank()
    ) 
}

lang_plotter(mods$languages$mdt, "Melodic Discrimination", "Language") + 
lang_plotter(mods$languages$mpt, "Mistuning Perception") + 
lang_plotter(mods$languages$cabat, "Beat Alignment") +
  plot_layout(guides = "collect") & 
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = .5, size = 16))

```{r OLD-Figure4, fig.width = 10, fig.height = 6, eval=FALSE, include=FALSE}

lang_plotter <- function(data_x, x_lab, y_lab) {
  ggplot(data = confirm_plot_data %>%
           filter(musicLessons == "No")) +
    geom_boxplot(aes(y = reorder(language, {{data_x}}, median), x = {{data_x}},
                     fill = factor(Tone, levels = c("Non-tonal","Pitch-accented", "Tonal"))), outlier.shape=NA) +
    scale_fill_manual(values=c("#85C0F9", "#A95AA1", "#F5793A"),
                      labels = c("Non-tonal","Pitch-accented", "Tonal"),
                      name = NULL) +
    geom_hline(yintercept = miq_confirm_filtered %>% group_by(country) %>% summarise(avg = mean(mdt)) %>% pull(avg) %>% median(),
               linetype = "dotted", color = "black") +
    lims(x = c(-3,3)) +
    labs(x = NULL,
         y = y_lab, 
         title = x_lab) +
    theme_minimal() +
    theme(axis.text.y= element_blank(),
          axis.title = element_text(size = 16),
          axis.ticks.y = element_blank(),
          legend.text = element_text(size = 12),
          panel.grid = element_blank()
    ) 
}

lang_plotter(mdt, "Melodic Discrimination", "Languages ranked by median score") +
  lang_plotter(mpt, "Mistuning Perception", NULL) +
  lang_plotter(cabat, "Beat Alignment", NULL) + 
  plot_layout(guides = "collect") & 
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = .5, size = 16))

```{r New-SI-Figure1, fig.width = 12, fig.height = 7}

size_dat <- miq_confirm_filtered %>%
  count(language) %>%
  mutate(
    language = case_when(
      language == "Chinese/Mandarin" ~ "Mandarin",
      language == "Chinese/Cantonese/Yue" ~ "Cantonese",
      language == "Chinese/Taiwanese/Min Nan/Hokkien" ~ "Hokkien",
      TRUE ~ language
    )
  ) %>%
  select(language, confirmatory = n) %>%
  full_join(., languages %>%
              mutate(
                language = case_when(
                  language == "Chinese/Mandarin" ~ "Mandarin",
                  language == "Chinese/Cantonese/Yue" ~ "Cantonese",
                  language == "Chinese/Taiwanese/Min Nan/Hokkien" ~ "Hokkien",
                  TRUE ~ language
                )
              ))

ggplot(size_dat) +
  theme_apa() +
  geom_text_repel(
    aes(
      label = language,
      x = Tone,
      y = confirmatory,
      color = Tone,
      size = confirmatory
    ),
    min.segment.length = 999, # removing segments
    position = position_jitter(width = 0.3)
  ) +
  scale_color_manual(values=color_scheme)+
  scale_y_log10(labels = comma) +
  scale_x_discrete(labels = c(
    "<i style='color:#85C0F9;'>Non-tonal</i>",
    "<i style='color:#A95AA1;'>Pitch-accented</i>",
    "<i style='color:#F5793A;'>Tonal</i>"),
    name = NULL) +
  scale_size(range = c(4, 20), name = "Sample Size") +
  theme(
    axis.title.y = element_text(size = 20),
    axis.text.x = element_markdown(size = 16, face = "bold"),
    axis.text.y = element_text(size = 16),
    legend.position = "none"
  ) +
  labs(y = "Sample Size", x = "Language Type", color = "Language Type")

```{r FigureStemp, fig.width=10, fig.height = 4}

plot <- fig3_data %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 1, alpha = 1, size = .3) +
  geom_point(aes(x = exploratory, y = confirmatory, color = Tone),
             alpha = 0.8, size = 2) +
  facet_wrap(
    ~ factor(test, levels = c("mdt", "mpt", "cabat")), 
    labeller = labeller(.rows = c("mdt" = "Melodic Discrimination", "mpt" = "Mistuning Perception", "cabat" = "Beat Alignment"))
  ) +
  geom_hline(yintercept = 0, lty = "dotted", alpha = .6) +
  geom_vline(xintercept = 0, lty = "dotted", alpha = .6) +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        aspect.ratio = 1,
        strip.text = element_text(size = 16),
        panel.spacing = unit(2, "lines"),
        legend.text = element_text(size = 12)) +
  lims(x = c(-.4, 1), y = c(-.4, 1)) +
  labs(x = "Exploratory mean score",
       y = "Confirmatory mean score")+
  scale_color_manual(values=c("#85C0F9", "#A95AA1", "#F5793A"), labels = c("Non-tonal","Pitch-accented", "Tonal"))

# extra custom code to deal with clipping in facet labels...
fixed_plot <- ggplotGrob(plot)

for(i in which(grepl("strip-t", fixed_plot$layout$name))){
  fixed_plot$grobs[[i]]$layout$clip <- "off"
}

grid::grid.draw(fixed_plot)

```{r FigureS1a, fig.width = 7, fig.height = 8, include=FALSE}

@@

format_language_label <- function(data, add_count = FALSE) {
  data <- data |> 
    mutate(level_clean = case_when(
      level == "Chinese/Mandarin" ~ "Mandarin",
      level == "Chinese/Cantonese/Yue" ~ "Yue",
      level == "Chinese/Other dialects" ~ "Other Chinese languages",
      level == "Chinese/Taiwanese/Min Nan/Hokkien" ~ "Hokkien",
      TRUE ~ level
    ))

@@

p1 <- lang_plotter2(format_language_label(mods$languages$mdt, TRUE), "Melodic Discrimination")

\clearpage
```{r FigureS1b, fig.width = 7, fig.height = 8, include=FALSE}

p2 <- lang_plotter2(format_language_label(mods$languages$mpt, TRUE), "Mistuning Perception")

\clearpage
```{r FigureS1c, fig.width = 7, fig.height = 8, include=FALSE}

p3 <- lang_plotter2(format_language_label(mods$languages$cabat, TRUE), "Beat Alignment")

\newpage
```{r figureTest, fig.width = 21.2, fig.height = 15, out.extra='angle=90', out.width="100%", out.height="100%"}

@@

\clearpage
```{r FigureS1, fig.height=3, eval=FALSE}

ggplot(headphone_score) +
  geom_bar(aes(score)) +
  theme_light() +
  geom_vline(aes(xintercept = mean(headphone_score$score)), color = "red", linetype = "longdash", size = 1.5) +
  labs(x = "Headphone Test Score")

@@

clean_data_for_table <- function(meta_data, dataname, add_rows = FALSE) {
  out <- bind_cols(meta_data$clean, as_tibble(meta_data)) |> 
    select(
      Study, Measure, `Tonal Sample` = Tonal, `Non-tonal Sample` = `Non-tonal`, TE, SMD = hedge_g, lower, upper, w.random
    ) |> 
    mutate(Power = scales::percent(meta_data$Power, scale = 100, accuracy = 1L), .before = TE) |> 
    mutate(
      Estimate = r2(TE), 
      across(c(lower, upper), r2, .names = "{.col}_clean"),
      `95% CI` = str_c("[", lower_clean, ", ", upper_clean, "]"),
      Estimate = str_c(Estimate, " ", `95% CI`),
      overall = meta_data$TE.fixed,
      Weight = scales::percent(weights(meta_data)$p.random, scale = 1, accuracy = 1L),
      Study = str_remove_all(Study, "\\\\") # remove escape characters
    ) |>
    arrange(desc(TE)) |> 
    bind_rows(tibble(TE = meta_data$TE.fixed, Study = "Overall")) |> 
    # add a couple blank rows at the end
    mutate(dataname = dataname)

@@

  ggplot(dat, aes(y = row, x = TE, xmin = lower, xmax = upper,
                         shape = overall, size = overall, stroke = overall, colour = overall)) + 
    # create vertical line annotation to indicate fixed effects
    annotate("segment", x = melodic_effect, xend = melodic_effect, y = 34.5, yend = 46.5, lty = "dotted") +
    annotate("segment", x = pitch_effect, xend = pitch_effect, y = 11.5, yend = 31.5, lty = "dotted") +
    annotate("segment", x = rhythm_effect, xend = rhythm_effect, y = 1.5, yend = 8.5, lty = "dotted") +
    # add text annotation for the fixed effects
    annotate("text", x = melodic_effect + 0.55, xend = melodic_effect + 0.55, y = 34, yend = 34, label = r2(melodic_effect)) +
    annotate("text", x = pitch_effect + 0.55, xend = pitch_effect + 0.55, y = 11, yend = 11, label = r2(pitch_effect)) +
    annotate("text", x = rhythm_effect + 0.6, xend = rhythm_effect + 0.6, y = 1, yend = 1, label = r2(rhythm_effect)) +
    geom_vline(xintercept = 0) +
    geom_point() +
    geom_errorbar(size = 0.6) +
    scale_colour_manual(values = c("grey50", "black")) +
    scale_discrete_manual(aesthetics = "stroke", values = c(0.8, 1.5)) +
    scale_shape_manual(values = c(19,5)) +
    scale_size_manual(values = c(2, 5)) +
    coord_cartesian(ylim = c(1.75, 45)) +
    theme_classic() + 
    theme(
      legend.position = "none",
      axis.text.y = element_blank(),
      axis.title.y = element_blank(),
      axis.line.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.x = element_blank()
    )
}

@@

  forest_plot_creator(left_side_data = select(combined, 1:5) |> mutate(Study = ifelse(Study == "Overall", " ",Study)),
                      right_side_data = select(combined, Estimate, Weight),
                      center_ggplot = center_plot,
                      top_offset = top_offset,
                      bottom_offset = bottom_offset,
                      left_offset = left_offset,
                      right_offset = right_offset,
                      file_path = here::here("viz", "temp", filename))
}

@@

# meta_fig_assembler(melodic.gen.random, "melodic", "melodic_meta-plot.png", top_offset = 0.005, bottom_offset = -0.035, right_offset = -0.015)

# MPT
pitch.gen.random$clean <- pitch.gen.random$data |>
  mutate( 
    Tonal = str_c(Tonal_N, " (", Non_CM_tonal, ")"), 
    `Non-tonal` = str_c(Non_tonal_N, " (", Non_E_nontonal, ")")
  ) |> 
  mutate(
    Study = case_when(
      `Non-tonal` == "11 (Portuguese, 1)" ~ "Pfordresher & Brown (2009), Study 2",
      `Non-tonal` == "17 (No)" && Study == "Giuliano et al. (2011)" ~ "Giuliano et al. (2011), Study 1",
      `Non-tonal` == "5 (No)" ~ "Bidelman et al. (2011), Study 2",
      Measure == "Mistuning detection (Study2)" ~ "Wong et al. (2012), Study 2",
      Measure == "Mistuned detection (Study1)" ~ "Wong et al. (2012), Study 1",
      TRUE ~ Study
    ),
    Measure = case_when(
      Measure == "Mistuning detection (Study2)" ~ "Mistuning detection",
      Measure == "Mistuned detection (Study1)" ~ "Mistuned detection",
      TRUE ~ Measure
    )
  ) |>
  mutate(
    Measure = if_else(Measure == "Interval discrimination/Musical Task", "Interval discrimination", Measure),
    Tonal = case_when(
      Study == "Peretz et al. (2011)" ~ "18 Mandarin; 4 Vietnamese; 2 Cantonese",
      Study == "Tong et al. (2018)" ~ "15 Cantonese",
      Study == "Pfordresher \\& Brown (2009)" ~ "6 Vietnamese; 4 Mandarin; 2 Cantonese",
      Study == "Pfordresher & Brown (2009), Study 2" ~ "11 Mandarin",
      Study == "Wong et al. (2012), Study 1" ~ "408 Cantonese",
      Study == "Wong et al. (2012), Study 2" ~ "408 Cantonese",
      Study == "Zheng \\& Samuel (2018)" ~ "24 Mandarin",
      Study == "Jasmin et al. (2021)" ~ "31 Cantonese",
      Study == "Giuliano et al. (2011), Study 1" ~ "17 Mandarin",
      Study == "Stevens et al. (2013)" ~ "24 Thai",
      Study == "Bidelman et al. (2011)" ~ "11 Mandarin",
      Study == "Tong et al. (2018)" ~ "30 Cantonese",
      Study == "Bent et al. (2006)"~ "13 Mandarin",
      Study == "Giuliano et al. (2011)" ~ "16 Mandarin",
      Study == "Hutka et al. (2015)" ~ "18 Cantonese",
      Study == "Bidelman et al. (2011), Study 2" ~ "5 Mandarin",
      Study == "Bidelman et al. (2013)" ~ "18 Cantonese",
      TRUE ~ Tonal
    ),
    `Non-tonal` = case_when(
      Study == "Peretz et al. (2011)" ~ "25 'non-tonal' (likely French/English)",
      Study == "Tong et al. (2018)" ~ "15 English",
      Study == "Pfordresher \\& Brown (2009)" ~ "12 English",
      Study == "Pfordresher & Brown (2009), Study 2" ~ "10 English; 1 Portuguese",
      Study == "Wong et al. (2012), Study 1" ~ "154 English/French",
      Study == "Wong et al. (2012), Study 2" ~ "154 English/French",
      Study == "Jasmin et al. (2021)" ~ "36 English; 26 Spanish",
      Study == "Zheng \\& Samuel (2018)" ~ "24 English, 24 Korean",
      Study == "Giuliano et al. (2011), study 1" ~ "16 'Non-tonal'",
      Study == "Stevens et al. (2013)" ~ "24 English",
      Study == "Bidelman et al. (2011)" ~ "11 English",
      Study == "Tong et al. (2018)" ~ "11 English; 19 'Non-tonal'",
      Study == "Bent et al. (2006)"~ "13 English",
      Study == "Giuliano et al. (2011)" ~ "16 'Non-tonal'",
      Study == "Hutka et al. (2015)" ~ "21 English",
      Study == "Bidelman et al. (2011), Study 2" ~ "5 English",
      Study == "Bidelman et al. (2013)" ~ "18 English",
      TRUE ~ `Non-tonal`
    )
  )

@@

# meta_fig_assembler(pitch.gen.random, "pitch", "fine-pitch_meta-plot.png", top_offset = 0.028, bottom_offset = -0.016, right_offset = -0.015)

# Beat processing
# MPT
rhythm.gen.random$clean <- rhythm.gen.random$data |>
  mutate( 
    Tonal = str_c(Tonal_N, " (", Non_CM_tonal, ")"), 
    `Non-tonal` = str_c(Non_tonal_N, " (", Non_E_nontonal, ")")
  ) |> 
    mutate(
    Study = case_when(
      Measure == "Off-beat detection (Study2)" ~ "Wong et al. (2012), Study 2",
      Measure == "Off-beat detection (Study1)" ~ "Wong et al. (2012), Study 1",
      TRUE ~ Study
    )
  ) |> 
  mutate(
    Measure = if_else(Measure == "Interval discrimination/Musical Task", "Interval discrimination", Measure),
    Tonal = case_when(
      Study == "Swaminathan et al (2021)" ~ "104 Chinese languages; 3 Vietnamese",
      Study == "Peretz et al. (2011)" ~ "18 Mandarin; 4 Vietnamese; 2 Cantonese",
      Study == "Wong et al. (2012), Study 1" ~ "408 Cantonese",
      Study == "Wong et al. (2012), Study 2" ~ "22 Cantonese",
      Study == "Ngo et al. (2016)" ~ "8 Vietnamese",
      Study == "Choi (2021)" ~ "30 Cantonese",
      Study == "Jasmin et al. (2021)" ~ "31 Mandarin",
      TRUE ~ Tonal
    ),
    `Non-tonal` = case_when(
      Study == "Swaminathan et al (2021)" ~ "366 English; 42 various non-tonal languages",
      Study == "Peretz et al. (2011)" ~ "25 'non-tonal' (likely French/English)",
      Study == "Wong et al. (2012), Study 1" ~ "154 English/French",
      Study == "Wong et al. (2012), Study 2" ~ "26 English",
      Study == "Ngo et al. (2016)" ~ "8 English",
      Study == "Choi (2021)" ~ "30 English",
      Study == "Jasmin et al. (2021)" ~ "62 English and Spanish",
      TRUE ~ `Non-tonal`
    )
  )

@@

\clearpage
```{r meta-analysis, fig.height=4, fig.width=18, out.extra='angle=90'}

meta_fig_assembler2(melodic.gen.random, pitch.gen.random, rhythm.gen.random,
                    "mega_meta-plot.pdf", top_offset = 0.072, bottom_offset = -0.02, right_offset = -0.015)

@@

```{r FigureS2, fig.height=4, fig.width=12}

>>>>

# save figure outputs here
knitr::opts_chunk$set(fig.path = here("viz", "figures", ""), dpi = 500)

@@

```{r Figure2, fig.width = 12, fig.height = 6}

@@

@@

```{r Figure3, fig.width = 10, fig.height = 4}

@@

mods$total_mix_full$mdt$marginal %>% 
  bind_rows(., mods$total_mix_full$mpt$marginal) %>% 
  bind_rows(., mods$total_mix_full$cabat$marginal) %>% 
  pivot_wider(names_from = group, values_from = c(predicted:conf.high)) %>% 
  mutate(tone = factor(x, levels = c("Non-tonal", "Pitch-accented", "Tonal")),
         test = factor(test, levels = c("mdt", "mpt", "cabat"))) %>% 
  ggplot(.,
         aes(x = test, y = predicted_No, color = tone)) +
  geom_hline(aes(yintercept = 0), color = "black", alpha = 0.7, linetype = "dashed") +
  geom_errorbar(aes(ymax = conf.high_No, ymin = conf.low_No, color = tone), position = position_dodge(.5), width = .2, key_glyph = draw_key_rect) +
  geom_errorbar(aes(ymax = conf.high_Yes, ymin = conf.low_Yes, color = tone), position = position_dodge(.5), width = .2, alpha = .5, key_glyph = draw_key_rect) +
  geom_point(position = position_dodge(.5), size = 2) +
  geom_point(data = test, aes(x = test, y = predicted, shape = group), inherit.aes = FALSE, alpha = 0) +
  scale_shape_manual(values = c(19, 17), name = "test",
                     labels = c("Without Music Lessons", "With Music Lessons")) +
  geom_point(aes(y = predicted_Yes), position = position_dodge(.5), size = 2, alpha = .5, pch = 17) +
  geom_linerange(aes(ymax = predicted_Yes, ymin = predicted_No, color = tone), position = position_dodge(.5), linetype = "dashed", alpha = .5) +
  scale_x_discrete(labels = c("Melodic Discrimination","Mistuning Perception", "Beat Alignment"), position = "top") +
  scale_color_manual(values=color_scheme, labels = c("Non-tonal","Pitch-accented","Tonal")) +
  guides(shape = guide_legend(override.aes = list(alpha = .8, size = 4))) +
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    axis.text.x = element_text(size = 16),
    panel.grid.major.y = element_line(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(), 
    legend.position = "bottom",
    legend.text = element_text(size = 12))

@@

```{r Figure4, fig.width = 21.2, fig.height = 15, out.extra='angle=90', out.width="100%", out.height="100%"}

@@

format_language_label <- function(data, add_count = FALSE) {
  data <- data |> 
    mutate(level_clean = case_when(
      level == "Chinese/Mandarin" ~ "Mandarin",
      level == "Chinese/Cantonese/Yue" ~ "Cantonese",
      level == "Chinese/Other languages" ~ "Other Chinese languages",
      level == "Chinese/Taiwanese/Min Nan/Hokkien" ~ "Hokkien",
      TRUE ~ level
    ))

@@

p1 <- lang_plotter2(format_language_label(mods$languages$mdt, TRUE), "Melodic Discrimination")
p2 <- lang_plotter2(format_language_label(mods$languages$mpt, TRUE), "Mistuning Perception")
p3 <- lang_plotter2(format_language_label(mods$languages$cabat, TRUE), "Beat Alignment")

@@

\clearpage
```{r FigureS1, fig.height=3, fig.width=6}
headphone_score <- read.csv(here("data", "headphone_score.csv"))

ggplot(headphone_score) +
  geom_bar(aes(score), colour = "black", fill = "grey20") +
  scale_y_continuous(labels = comma) +
  scale_x_continuous(labels = 0:6, breaks = 0:6) +
  geom_vline(aes(xintercept = mean(score)), color = "red", linetype = "longdash", size = 1.5) +
  labs(
    y = "Participant Count",
    x = "Headphone Test Score"
  ) +
  theme_minimal()

@@

clean_data_for_table <- function(meta_data, dataname, add_rows = FALSE) {
  out <- bind_cols(meta_data$clean, as_tibble(meta_data)) |> 
    select(
      Study, Measure, `Tonal Sample` = Tonal, `Non-tonal Sample` = `Non-tonal`, TE, SMD = hedge_g, lower, upper, w.random
    ) |> 
    mutate(Power = scales::percent(meta_data$Power, scale = 100, accuracy = 1L), .before = TE) |> 
    mutate(
      Estimate = r2(TE), 
      across(c(lower, upper), r2, .names = "{.col}_clean"),
      `95% CI` = str_c("[", lower_clean, ", ", upper_clean, "]"),
      Estimate = str_c(Estimate, " ", `95% CI`),
      overall = meta_data$TE.random,
      Weight = scales::percent(weights(meta_data)$p.random, scale = 1, accuracy = 1L),
      Study = str_remove_all(Study, "\\\\") # remove escape characters
    ) |>
    arrange(desc(TE)) |> 
    bind_rows(tibble(TE = meta_data$TE.random, Study = "Overall")) |> 
    # add a couple blank rows at the end
    mutate(dataname = dataname)

@@

  ggplot(dat, aes(y = row, x = TE, xmin = lower, xmax = upper,
                         shape = overall, size = overall, stroke = overall, colour = overall)) + 
    # create vertical line annotation to indicate fixed effects
    annotate("segment", x = melodic_effect, xend = melodic_effect, y = 34.5, yend = 46.5, lty = "dotted") +
    annotate("segment", x = pitch_effect, xend = pitch_effect, y = 11.5, yend = 31.5, lty = "dotted") +
    annotate("segment", x = rhythm_effect, xend = rhythm_effect, y = 1.5, yend = 8.5, lty = "dotted") +
    # add text annotation for the fixed effects
    annotate("text", x = melodic_effect + 0.67, xend = melodic_effect + 0.67, y = 35, yend = 35, label = r2(melodic_effect)) +
    annotate("text", x = pitch_effect + 0.67, xend = pitch_effect + 0.67, y = 11, yend = 11, label = r2(pitch_effect)) +
    annotate("text", x = rhythm_effect + 0.72, xend = rhythm_effect + 0.72, y = 1, yend = 1, label = r2(rhythm_effect)) +
    geom_vline(xintercept = 0) +
    geom_point() +
    geom_errorbar(size = 0.6) +
    scale_colour_manual(values = c("grey50", "black")) +
    scale_discrete_manual(aesthetics = "stroke", values = c(0.8, 1.5)) +
    scale_shape_manual(values = c(19,5)) +
    scale_size_manual(values = c(2, 5)) +
    coord_cartesian(ylim = c(1.75, 46)) +
    theme_classic() + 
    theme(
      legend.position = "none",
      axis.text.y = element_blank(),
      axis.title.y = element_blank(),
      axis.line.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.x = element_blank()
    )
}

@@

  forest_plot_creator(left_side_data = select(combined, 1:5) |> mutate(Study = ifelse(Study == "Overall", " ",Study)),
                      right_side_data = select(combined, Estimate, Weight),
                      center_ggplot = center_plot,
                      top_offset = top_offset,
                      bottom_offset = bottom_offset,
                      left_offset = left_offset,
                      right_offset = right_offset,
                      file_path = here::here("viz", "figures", filename))
}

@@

# meta_fig_assembler(melodic.gen.random, "melodic", "melodic_meta-plot.png", top_offset = 0.005, bottom_offset = -0.035, right_offset = -0.015)
```

```{r}
# MPT
pitch.gen.random$clean <- pitch.gen.random$data |>
  mutate( 
    Tonal = str_c(Tonal_N, " (", Non_CM_tonal, ")"), 
    `Non-tonal` = str_c(Non_tonal_N, " (", Non_E_nontonal, ")")
  ) |> 
  mutate(
    Study = case_when(
      `Non-tonal` == "11 (Portuguese, 1)" & Measure == "Interval discrimination" ~ "Pfordresher \\& Brown (2009), Study 2",
      `Non-tonal` == "11 (Portuguese, 1)" & Measure == "Note discrimination" ~ "Pfordresher \\& Brown (2009), Study 2",
      Study == "Pfordresher \\& Brown (2009)" & Measure == "Interval discrimination" ~ "Pfordresher \\& Brown (2009), Study 1",
      Study == "Pfordresher \\& Brown (2009)" ~ "Pfordresher \\& Brown (2009), Study 1",
      `Non-tonal` == "5 (No)" ~ "Bidelman et al. (2011), Study 2",
      Measure == "Mistuning detection (Study2)" ~ "Wong et al. (2012), Study 2",
      Measure == "Mistuned detection (Study1)" ~ "Wong et al. (2012), Study 1",
      TRUE ~ Study
    ),
    Measure = case_when(
      Measure == "Mistuning detection (Study2)" ~ "Mistuning detection",
      Measure == "Mistuned detection (Study1)" ~ "Mistuned detection",
      TRUE ~ Measure
    )
  ) |>
  mutate(
    Measure = if_else(Measure == "Interval discrimination/Musical Task", "Interval discrimination", Measure),
    Tonal = case_when(
      Study == "Peretz et al. (2011)" ~ "18 Mandarin; 4 Vietnamese; 2 Cantonese",
      Study == "Tong et al. (2018)" ~ "15 Cantonese",
      Study == "Pfordresher \\& Brown (2009), Study 1" ~ "6 Vietnamese; 4 Mandarin; 2 Cantonese",
      Study == "Pfordresher & Brown (2009), Study 2" ~ "11 Mandarin",
      Study == "Wong et al. (2012), Study 1" ~ "408 Cantonese",
      Study == "Wong et al. (2012), Study 2" ~ "22 Cantonese",
      Study == "Zheng \\& Samuel (2018)" ~ "24 Mandarin",
      Study == "Jasmin et al. (2021)" ~ "31 Cantonese",
      Study == "Giuliano et al. (2011), Study 1" ~ "17 Mandarin",
      Study == "Stevens et al. (2013)" ~ "24 Thai",
      Study == "Bidelman et al. (2011)" ~ "11 Mandarin",
      Study == "Tong et al. (2018)" ~ "30 Cantonese",
      Study == "Bent et al. (2006)"~ "13 Mandarin",
      Study == "Giuliano et al. (2011)" ~ "16 Mandarin",
      Study == "Hutka et al. (2015)" ~ "18 Cantonese",
      Study == "Bidelman et al. (2011), Study 2" ~ "5 Mandarin",
      Study == "Bidelman et al. (2013)" ~ "18 Cantonese",
      TRUE ~ paste0(Tonal_N, " ", Tonal_language)
    ),
    `Non-tonal` = case_when(
      Study == "Peretz et al. (2011)" ~ "25 'non-tonal' (likely French/English)",
      Study == "Tong et al. (2018)" ~ "15 English",
      Study == "Pfordresher \\& Brown (2009)" ~ "12 English",
      Study == "Pfordresher \\& Brown (2009), Study 2" ~ "10 English; 1 Portuguese",
      Study == "Wong et al. (2012), Study 1" ~ "154 English/French",
      Study == "Wong et al. (2012), Study 2" ~ "26 English/French",
      Study == "Jasmin et al. (2021)" ~ "36 English; 26 Spanish",
      Study == "Zheng \\& Samuel (2018)" ~ "24 English, 24 Korean",
      Study == "Giuliano et al. (2011), study 1" ~ "16 'Non-tonal'",
      Study == "Stevens et al. (2013)" ~ "24 English",
      Study == "Bidelman et al. (2011)" ~ "11 English",
      Study == "Tong et al. (2018)" ~ "11 English; 19 'Non-tonal'",
      Study == "Bent et al. (2006)"~ "13 English",
      Study == "Giuliano et al. (2011)" ~ "16 'Non-tonal'",
      Study == "Hutka et al. (2015)" ~ "21 English",
      Study == "Bidelman et al. (2011), Study 2" ~ "5 English",
      Study == "Bidelman et al. (2013)" ~ "18 English",
      TRUE ~ paste0(Non_tonal_N, " ", Comparison_language)
    )
  )

@@

# meta_fig_assembler(pitch.gen.random, "pitch", "fine-pitch_meta-plot.png", top_offset = 0.028, bottom_offset = -0.016, right_offset = -0.015)
```

```{r}
# Beat processing
# MPT
rhythm.gen.random$clean <- rhythm.gen.random$data |>
  mutate( 
    Tonal = str_c(Tonal_N, " (", Non_CM_tonal, ")"), 
    `Non-tonal` = str_c(Non_tonal_N, " (", Non_E_nontonal, ")")
  ) |> 
    mutate(
    Study = case_when(
      Measure == "Off-beat detection (Study2)" ~ "Wong et al. (2012), Study 2",
      Measure == "Off-beat detection (Study1)" ~ "Wong et al. (2012), Study 1",
      TRUE ~ Study
    )
  ) |> 
  mutate(
    Measure = if_else(Measure == "Interval discrimination/Musical Task", "Interval discrimination", Measure),
    Tonal = case_when(
      Study == "Swaminathan et al (2021)" ~ "104 Chinese languages; 3 Vietnamese",
      Study == "Peretz et al. (2011)" ~ "18 Mandarin; 4 Vietnamese; 2 Cantonese",
      Study == "Wong et al. (2012), Study 1" ~ "408 Cantonese",
      Study == "Wong et al. (2012), Study 2" ~ "22 Cantonese",
      Study == "Ngo et al. (2016)" ~ "8 Vietnamese",
      Study == "Choi (2021)" ~ "30 Cantonese",
      Study == "Jasmin et al. (2021)" ~ "31 Mandarin",
      TRUE ~ Tonal
    ),
    `Non-tonal` = case_when(
      Study == "Swaminathan et al (2021)" ~ "366 English; 42 various non-tonal languages",
      Study == "Peretz et al. (2011)" ~ "25 'non-tonal' (likely French/English)",
      Study == "Wong et al. (2012), Study 1" ~ "154 English/French",
      Study == "Wong et al. (2012), Study 2" ~ "26 English",
      Study == "Ngo et al. (2016)" ~ "8 English",
      Study == "Choi (2021)" ~ "30 English",
      Study == "Jasmin et al. (2021)" ~ "62 English and Spanish",
      TRUE ~ `Non-tonal`
    )
  )

@@

\clearpage
```{r Figure1, fig.height=4, fig.width=18, out.extra='angle=90'}

meta_fig_assembler2(melodic.gen.random, pitch.gen.random, rhythm.gen.random,
                    "meta-plot.pdf", top_offset = 0.07, bottom_offset = -0.02, right_offset = -0.015)

@@

```{r FigureS2, fig.height=8, fig.width=12}

permutation_plot <- function(data, subtitle, fill_col, title = NULL) {
  ggplot(tibble(x = data$null), aes(x)) + 
    geom_histogram(colour = "black", fill = colorspace::lighten(fill_col, 0.9)) + 
    geom_vline(xintercept = data$actual, lty = "dotted", colour = "red") +
    annotate("text", x = data$actual + 0.002, y = 1100, label = paste("p =", data$p), hjust = 0) +
    labs(
      y = NULL,
      x = "Classification Accuracy",
      title = title,
      subtitle = subtitle
      ) +
    coord_cartesian(clip = "off") +
    theme_classic() + 
    theme(
      plot.title = element_text(hjust = 0.5, size = 15),
      plot.subtitle = element_text(hjust = 0.5),
      axis.line.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.text.y = element_blank()
    )
}
